A Case Study in Preserving a High Energy Physics Application

### 2014-01-24 paper.tex
new pics and new sequence

\section{Introduction of the exmaple}

@@

\begin{figure}
\centering
\epsfig{file=data-process.eps, height=2.8in, width=3in}
\caption{Data Processing Procedures}
\label{fig:data-process}
\end{figure}

The data processing procedures are shown in Figure~\ref{fig:data-process}.

@@

\subsection{Source and Size of Data and Software}

The software sources are rich, including CMSSW, Git, HTTP and one personal main page. The size of software from each source is shown in Table~\ref{table:software-source-size}.

As for the experiment data, Matthias copies the subset of T3 data from grid and stores the data into HDFS mounted as one local file system. The total size of data stored in HDFS is 33TB (*need to rethink).

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        Version 1\\ \hline
        \\
        1. Create CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3... \\
        2. Install BEAN packages: \\
            \hspace{9pt} https://github.com/cms-ttH/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://dwekptrack... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform actual analysis \\ 
        \\ \hline
        Version 2\\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3...) \\
        module load git \\        
        cmsenv \\ 
        cvs login \\
        cvs co UserCode/Bicocca/... \\
        git clone... \\
        scram b -j32 \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        \#the experiment data is from HDFS \\
        roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        Version 3\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \# list of indirect software dependencies \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
        cmsenv \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        roaster data/generic\_ttl.yaml \\
        \\ \hline
        Version 4\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \#declaration of environment variables\\
        \#data dependencies\\
        \#direct and indirect software dependencies\\
        \#software build and install commands\\
        \#actual analysis program\\ 
        \\ \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

\section{Solution 1 to Repeat the Program}
In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment. In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links. The Version 1 of Table~\ref{table:scripts} illstrates his email.

@@

\section{Solution 2 to Repeat the Program}
One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly. Another possible solution is let the new user directly operate on the machine the original author used. As for the complexity of jumping between multiple web links, people may suggest that letting the original author generate one clear script including all the contents from different web links.

@@

The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. About half of the total execution time is consumed to prepare relevant software environment. The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.

@@

\section{Solution 3 to Repeat the Program}
\subsection{Dependencies of the Program}

\begin{figure*}
\centering
\epsfig{file=overview-of-architecture.eps, height=4in, width=6.5in}
\caption{Overview of Architecture}
\label{fig:Overview of architecture}
\end{figure*}

Figure~\ref{fig:Overview of architecture} illustrates all the dependencies
involved in the program, which can be divided into two categories: clear
dependencies and implicit dependencies. Clear dependencies include data
dependencies and direct software dependencies which can be extracted directly
from the analysis program. Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one soft link file further referring to
another name named File2. 
The implicit dependencies also refers to some files under /pscratch, which is one local mount point of one PanFS clustered file system with the size of 206TB.

Implication: One mechanism which can mine all the dependencies of the program is necessary.

\subsection{Working principle of Packaging Utility}

@@

\subsection{Workflow of Packaging Utility}
The workflow of generating one package for one analysis program is as follows.

@@

\subsection{Structure of Map File}

@@

\subsection{Evaluation of Solution 3}
The breakdown of execution time of the Solution 3 is illustrated in Table~\ref{table:time-3rd}. The time used to obtain file namelist and generate P1 is greatly longer than the execution time within the new package. however, the time consumption of file namelist acquisition and package generation is one-time. That is, once the package is generated, many users can directly obtain the package and repeat the experiment separately.

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Sub-Task & Time \\ \hline
    Obtain file namelist & 37min 51s \\ \hline
    Generate P1 & 13min 37s \\ \hline
    Re-run the program within P1 & 13min 5s \\ \hline
    \end{tabular}
    \caption{Time Breakdown of Solution 3}
    \label{table:time-3rd}
\end{table}

The data size of Solution 3 is shown in Table~\ref{table:datasize-3rd}. The
data categories is more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from /pscratch, /sbin, /lib and other
paths are also necessary for the reproduction of the program.

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data Size \\ \hline
    Hadoop & 20GB \\ \hline
    CMSSW\_5\_3\_11\_patch3 & 5.2MB \\ \hline
    pscratch & 119MB \\ \hline
    usr & 60MB \\ \hline
    Others (/sbin + ... + /lib) & 28.4MB \\ \hline
    Total & 20.213GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 3}
    \label{table:datasize-3rd}
\end{table}

\subsection{Discussion of Solution 3}

Under Solution 3, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction of it only needs
the necessary environment variables, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

%here is the new content-hmeng
The starting point of Solution 3 is one successful execution sandbox on the original machine. 
Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
The necessary scientific data will be copied into the target package.
The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
which can not be obtained through reading the analysis script. 
Parrot can obtain every dependency through trapping each system call.
Strictly speaking, the software concept and the scientific data concept are lost in Solution 3, because
the granularity of parrot is file.
The same thing happens to networked resources.
Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
As for the computing environment, Solution 3 notices the new user through the description information at the beginning of the script.
%the following subsection belongs to the "discussion of data and software
%preservation" section

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        Solution 3& grid & CMSSW Git HTTP & email \\ \hline
        Solution 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 3& package & package & shell script + packaging utility \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table*}

@@

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Comparison of different Solutions}
\subsection{Relationship of Different Solutions}
The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}. The aim is to make it easier to repeat one program through making the data and software preparation easier.

\subsection{ Data size Comparison of Solution 2 and 3}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data Size & Data Size \\
    & Solution 2 & Solution 3\\ \hline
    Hadoop & 33TB = 33792GB & 20GB \\ \hline
     CMSSW\_5\_3\_11\_patch3 & 562MB & 5.2MB \\ \hline
     Other data for Package & 207.4MB & N/A \\ \hline
     Total & 33792.562GB & 20.213GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 3}
    \label{table:datasize-2nd3rd}
\end{table}

\subsection{Execution Time Comparison of Solution 2 and 3}

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 3. The time consumption of the reproduction of one program from
different scholars kept the same under Solution 2, including software and data
preparation. However, under Solution 3, the data and software preparation is
one-time. The following reproduction of the same program only needs to obtain
one copy of the package and execute the actual experimental analysis directly.
Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 3. This localization of data speeds up the data analysis process, resulting the actual analysis time reducing from 31 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Task Category & Execution Time & Execution Time \\
    & Solution 2 & Solution 3\\ \hline
    Software Acquisition & 16min 15s & N/A \\ \hline
    Environment Building & 13min 21s  & 4s \\ \hline
    Obtain file namelist & N/A & 37min 51s \\ \hline
    Generate the package & N/A & 13min 37s \\ \hline
    Actual Analysis & 31min 44s & 13min 1s \\ \hline
    Total & 61min 20s & N/A \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 3}
    \label{table:time-2nd3rd}
\end{table}

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
\section{Discussion of Data and Software Preservation}
\subsection{Preservation Integration of Multiple Programs}
The Solution 3 can work well for the preservation and reproduction of one single program. However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software. Generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, that can integrate the preservation requirements of different analysis programs, become necessary.

@@

Another important factor of data and software preservation is the choice of
preservation granularity. In Solution 3, the preservation granularity is one
file, because Parrot virtual filesystem traps each system call and redirects
the access path of each file. As a result, during the packaging process, each
time only one file can be copied into the target package, which is
low-efficient. However, there are other options of preservation granularity.
The software is generally preserved in the unit of package inside the remote
repository, the packaging process of one experiment can adopt one package as
the unit. In addition, if the size of one whole software repository is small
and the access frequency of each package inside it is high, the granularity can
be set to the whole repository.

@@

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Data dependencies is easy to figured out. However, the situation of software dependencies is complex. The software
dependencies include OS, hardware platform, 
direct software dependencies and indirect software dependency which is dependent upon direct software dependencies.
The first
three categories are easy to deal with. The description of indirect software
dependencies needs more efforts. One solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.
Solution 3 odopts this solution, which is easy to implement, but leaves the
complex environment configuration to the new users.

@@

Directory is one list of files and subdirectories under it. At first, we only
copied the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, `ls /dirA` is one linux command to list the name of each item under
/dirA. Because the directory itself has the name list of items under it, only
the path of the directory was recorded into the namelist in the first phrase of
Solution 3. However, when we repeated the command `ls /dirA` using the
preserved package, it returned NULL because none of items under it existed in
the package. If one routine within the original program depends on the return
value of `ls /dirA`, the behavior of the whole program will become incorrect
and unpredictable.

To ensure the semantics of the original program, all the items under one directory must be copied
into the package. However, the
time and space overhead appears again. Currently, Solution 3 creates one item
with the same name but the size of zero for each item under /dirA. Another
solution is to introduce one database to preserve the metadata of each file and
directory.

@@

At the beginnig of our case study, we generated one package for Matthias's
example based on Solution 3. Several months later, the original machine meets
some problems and the access model of CMSSW was also modified. In this case, if
you want to repeat Matthias's example on the original machine, different 
configurations, including CMSSW\_ARCH, environment variables and CVS access
authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
%here is the new content-hmeng

>>>>

\section{Overview of Application}

@@

@@

\subsection{Key Observations of the Example}

\subsubsection{Complexity of Data and Software Dependencies}

\begin{figure}
\centering
\epsfig{file=dependencies.eps, height=3in, width=3.5in}
\caption{Dependencies}
\label{fig:dependencies}
\end{figure}

Figure~\ref{fig:dependencies} illustrates all the dependencies
involved in the program, which can be divided into two categories: clear
dependencies and implicit dependencies. Clear dependencies include data
dependencies and direct software dependencies which can be extracted directly
from the analysis program. The scientific data of this example comes from Grid. Direct software dependencies includes CMSSW, Git, HTTP and one personal main page.

Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one soft link file further referring to
another name named File2.
The implicit dependencies also refers to some files under /pscratch, which is one local mount point of one PanFS clustered file system with the size of 206TB.
And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.

\subsubsection{Size of Data and Software Dependencies}
The size of data and software dependencies is astonishing.
The size of the BEAN is 11.6TB, which is too large to be analyzed directly by the Tau Analysis program. However, after one preprocessing which only collects the events matching basic quality criteria, the data size is still very large, 43.3GB.

The size of software from each source is shown in Table~\ref{table:software-source-size}.

@@

\subsubsection{Complexity of the Program}
Complex data and software dependencies, complex environment building process, the large size of data and software involved in the Tau analysis, together with the access authority problem, determine the complexity of the program. 
In order to obtain the experimental data from the Grid, the author needs to install and config grid-control software. 
The access authority of the Grid is also necessary for the data acquisition.
The software acquisition from CMSSW, Git and HTTP and environment building process is time-consuming. The execution time of actual data analysis is about 30 minutes. However, the software acquisition and environment building time is about 30 minutes, which is very close to the execution time of actual data analysis. If the acquisition of experimental data is considered, the percentage of actual data analysis only occupies one small pertentage of the whole time consumption.
The size of data and software dependencies further complicate the program.

\subsubsection{Real Used Data and Software Size}

Even if the orginal data size referred by the program is astonishing, the size
of really used data and software is greatly smaller.
Figure~\ref{fig:data-code-size} illustrates the procedures of the Tau analysis.
After SBEAN, the data size is 43.3GB, however, the atual size of really used
data in the program is 20GB.  The same thend occurs to the size of software and
other dependencies. The size of CMSSW repository is 1.16TB, the size of
packages checked out from CMSSW is 449MB, and the size of actually used CMSSW
files is only 5.2MB. 
The total size of PanFS mounted as /pscratch is 206TB, however, the really used data from /pscratch is only 119MB.
We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Source & Original & Referred & Really Used \\ 
        & Size & Size & Size \\ \hline
        CMSSW & 1.16TB & 449MB & 5.2MB\\ \hline
        Git & 51MB & & \\ \hline
        Public HTTP & 52MB & & \\ \hline
        Private home page & 41KB & & \\ \hline
        HDFS & 33TB & 43.3GB & 20GB \\ \hline
        pscratch & 206TB & & 119MB \\ \hline
        Local Disk & & & 88.4MB \\ \hline     
    \end{tabular}
    \caption{Really Used Data and Software Size}
    \label{table:size-original-real}
\end{table}

\begin{figure}
\centering
\epsfig{file=data-code-size.eps, height=3in, width=3.5in}
\caption{Workflow of Tau Analysis}
\label{fig:data-code-size}
\end{figure}

\subsubsection{Stability of Dependencies}

The program involves obtaining software from the home page of another graduate
student from University of Notre Dame. However, the access authority of this
home page will termi nate after the graduation of the student. We need one
mechanism to 
evaluate the stability of each dependency must be evaluated to ensure the program can be 
repeated by others.

The stability of Grid is relatively higher. However, the
public web resources and personal home page is not stable. Too many factors
like the termination of one web site, the graduation of the home page's author,
would result in the failure of resource access. CMSSW, which seems to be
stable, in fact, also involves stability problems. CMSSW provides different
collections of accessible versions to different architectures. Transformation
from one architecture to another may result in the failure of accessing one
certain CMSSW version. At the beginning of our reseach, cvs supported
anonymous access of CMSSW outside of Cern. However, this anonymous access has
been cancelled now.

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        Version 1: Email\\ \hline
        \\
        1. Create CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3... \\
        2. Install BEAN packages: \\
            \hspace{9pt} https://github.com/cms-ttH/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://dwekptrack... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform actual analysis \\ 
        \\ \hline
        Version 2: Script\\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3...) \\
        module load git \\        
        cmsenv \\ 
        cvs login \\
        cvs co UserCode/Bicocca/... \\
        git clone... \\
        scram b -j32 \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        \#the experiment data is from HDFS \\
        roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        Version 3: Fine-Grained Toolkit\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \# list of indirect software dependencies \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
        cmsenv \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        roaster data/generic\_ttl.yaml \\
        \\ \hline
        Version 4\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \#declaration of environment variables\\
        \#data dependencies\\
        \#direct and indirect software dependencies\\
        \#software build and install commands\\
        \#actual analysis program\\ 
        \\ \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

\section{Preservation Strategies}

\begin{figure*}
\centering
\epsfig{file=version-evolution.eps, height=4in, width=6.5in}
\caption{Version Evolution}
\label{fig:version-evolution}
\end{figure*}

Figure~\ref{fig:version-evolution} illustrates the evolution history of different preservation strategies.

\subsection{Solution 1: Email}
In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment. In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links. The Version 1 of Table~\ref{table:scripts} illstrates his email.

@@

\subsection{Solution 2: Script}
One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly. Another possible solution is let the new user directly operate on the machine the original author used. As for the complexity of jumping between multiple web links, people may suggest that letting the original author generate one clear script including all the contents from different web links.

@@

@@

\subsection{Solution 3: Coarse-Grained Method}
%%

\subsection{Solution 4: Fine-Grained Toolkit}

\subsubsection{Working principle of Packaging Utility}

@@

\subsubsection{Workflow of Packaging Utility}
\begin{figure*}
\centering
\epsfig{file=workflow-parrot.eps, height=4in, width=6.5in}
\caption{Workflow of Solution 4}
\label{fig:workflow-parrot}
\end{figure*}

Figure~\ref{fig:workflow-parrot} illustrates the workflow of this solution.

The workflow of generating one package for one analysis program is as follows.

@@

\subsubsection{Structure of Map File}

@@

\subsubsection{Discussion of Solution 4}

Under Solution 4, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction of it only needs
the necessary environment variables, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

%here is the new content-hmeng
The starting point of Solution 4 is one successful execution sandbox on the original machine. 
Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
The necessary scientific data will be copied into the target package.
The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
which can not be obtained through reading the analysis script. 
Parrot can obtain every dependency through trapping each system call.
Strictly speaking, the software concept and the scientific data concept are lost in Solution 4, because
the granularity of parrot is file.
The same thing happens to networked resources.
Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
As for the computing environment, Solution 4 notices the new user through the description information at the beginning of the script.
%the following subsection belongs to the "discussion of data and software
%preservation" section

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
        Solution 2& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & shell script + packaging utility \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table*}

@@

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Evaluation}
\subsection{Relationship of Different Solutions}
The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}. The aim is to make it easier to repeat one program through making the data and software preparation easier.

\subsection{Evaluation of Solution 2}
The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. About half of the total execution time is consumed to prepare relevant software environment. The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.

\subsection{Evaluation of Solution 4}
The breakdown of execution time of the Solution 4 is illustrated in Table~\ref{table:time-3rd}. The time used to obtain file namelist and generate P1 is greatly longer than the execution time within the new package. however, the time consumption of file namelist acquisition and package generation is one-time. That is, once the package is generated, many users can directly obtain the package and repeat the experiment separately.

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Sub-Task & Time \\ \hline
    Obtain file namelist & 37min 51s \\ \hline
    Generate P1 & 13min 37s \\ \hline
    Re-run the program within P1 & 13min 5s \\ \hline
    \end{tabular}
    \caption{Time Breakdown of Solution 4}
    \label{table:time-3rd}
\end{table}

The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
data categories is more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from /pscratch, /sbin, /lib and other
paths are also necessary for the reproduction of the program.

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data Size \\ \hline
    Hadoop & 20GB \\ \hline
    CMSSW\_5\_3\_11\_patch3 & 5.2MB \\ \hline
    pscratch & 119MB \\ \hline
    usr & 60MB \\ \hline
    Others (/sbin + ... + /lib) & 28.4MB \\ \hline
    Total & 20.213GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

\subsection{ Data size Comparison of Solution 2 and 4}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data Size & Data Size \\
    & Solution 2 & Solution 4\\ \hline
    Hadoop & 33TB = 33792GB & 20GB \\ \hline
     CMSSW\_5\_3\_11\_patch3 & 562MB & 5.2MB \\ \hline
     Other data for Package & 207.4MB & N/A \\ \hline
     Total & 33792.562GB & 20.213GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

\subsection{Execution Time Comparison of Solution 2 and 4}

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 3. The time consumption of the reproduction of one program from
different scholars kept the same under Solution 2, including software and data
preparation. However, under Solution 4, the data and software preparation is
one-time. The following reproduction of the same program only needs to obtain
one copy of the package and execute the actual experimental analysis directly.
Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 4. This localization of data speeds up the data analysis process, resulting the actual analysis time reducing from 31 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Task Category & Execution Time & Execution Time \\
    & Solution 2 & Solution 4\\ \hline
    Software Acquisition & 16min 15s & N/A \\ \hline
    Environment Building & 13min 21s  & 4s \\ \hline
    Obtain file namelist & N/A & 37min 51s \\ \hline
    Generate the package & N/A & 13min 37s \\ \hline
    Actual Analysis & 31min 44s & 13min 1s \\ \hline
    Total & 61min 20s & N/A \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
\section{Discussion of Data and Software Preservation}
\subsection{Preservation Integration of Multiple Programs}
The Solution 4 can work well for the preservation and reproduction of one single program. However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software. Generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, that can integrate the preservation requirements of different analysis programs, become necessary.

@@

Another important factor of data and software preservation is the choice of
preservation granularity. In Solution 4, the preservation granularity is one
file, because Parrot virtual filesystem traps each system call and redirects
the access path of each file. As a result, during the packaging process, each
time only one file can be copied into the target package, which is
low-efficient. However, there are other options of preservation granularity.
The software is generally preserved in the unit of package inside the remote
repository, the packaging process of one experiment can adopt one package as
the unit. In addition, if the size of one whole software repository is small
and the access frequency of each package inside it is high, the granularity can
be set to the whole repository.

@@

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Data dependencies is easy to figured out. However, the situation of software dependencies is complex. The software
dependencies include OS, hardware platform, 
direct software dependencies and indirect software dependency which is dependent upon direct software dependencies.
The first
three categories are easy to deal with. The description of indirect software
dependencies needs more efforts. One solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.
Solution 4 odopts this solution, which is easy to implement, but leaves the
complex environment configuration to the new users.

@@

Directory is one list of files and subdirectories under it. At first, we only
copied the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, `ls /dirA` is one linux command to list the name of each item under
/dirA. Because the directory itself has the name list of items under it, only
the path of the directory was recorded into the namelist in the first phrase of
Solution 4. However, when we repeated the command `ls /dirA` using the preserved package, it returned NULL because none of items under it existed in
value of `ls /dirA`, the behavior of the whole program will become incorrect
and unpredictable.

To ensure the semantics of the original program, all the items under one directory must be copied
into the package. However, the
time and space overhead appears again. Currently, Solution 4 creates one item
with the same name but the size of zero for each item under /dirA. Another
solution is to introduce one database to preserve the metadata of each file and
directory.

@@

At the beginnig of our case study, we generated one package for Matthias's
example based on Solution 4. Several months later, the original machine meets
some problems and the access model of CMSSW was also modified. In this case, if
you want to repeat Matthias's example on the original machine, different 
configurations, including CMSSW\_ARCH, environment variables and CVS access
authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
%here is the new content-hmeng
